Illustrating Good Practice in {\LaTeX}

### 2022-03-07 articles/good_practice.tex
fixing colors one by one
still compiles lmao
it is Wednesday my dudes
it is Wednesday my dudes aaaaaaaaaagh
changed eq to eqn

This document is not a guide on how to use {\LaTeX}, since plenty of those already exist. Instead, what follows is an incoherent collection of examples that demonstrate good practice. For more of my awesome {\LaTeX} resources, visit \url{https://github.com/nkostin4/LaTeX-templates}.

@@

It is not hard to show that the eigenvalues of a Hermitian operator are real. Let $\ket{a}$ be an eigenstate of the Hermitian operator $A$ corresponding to eigenvalue $a$, then
\begin{equation}
    A \ket{a} = a \ket{a}. \label{eq:quantum:eigenvalueproblem}
\end{equation}

Then we have
\begin{equation}
    \braket{a|A|a} = \braket{a|a|a} = a\braket{a|a}. \label{eq:quantum:1}
\end{equation}

Taking the Hermitian conjugate of both sides of (\ref{eq:quantum:eigenvalueproblem}) gives
\begin{equation}
    \bra{a} A^{\dagger} = a^{*} \bra{a}.
\end{equation}

Then we also have
\begin{equation}
    \braket{a|A^{\dagger}|a} = a^{*} \braket{a|a} \label{eq:quantum:2}
\end{equation}

Since $A$ is Hermitian, we have $\braket{a|A^{\dagger}|a} = \braket{a|A|a}$. Then comparing (\ref{eq:quantum:1}) and (\ref{eq:quantum:2}) gives
\begin{equation*}
    \left( a - a^* \right) \braket{a|a} = 0.
\end{equation*}

@@

\begin{figure}[H]
\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
\centering
\begin{tikzpicture}[xscale=1,yscale=1]
    % Draw outside rectangle
    \draw[black] (-2,-2) rectangle (14,10);
    % Draw lattice points
    \foreach \a in {0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12}
    {
        \foreach \b in {0, 1, 2, 3, 4, 5, 6, 7, 8}
        {
            \filldraw[BLACK] (\a, \b) circle (2pt);
        }
    }
    \node[BLACK, anchor=north] at (0,0) {$x_0$};
    \node[BLACK, anchor=north] at (1,0) {$x_1$};
    \node[BLACK, anchor=north] at (11,0) {$x_{N - 1}$};
    \node[BLACK, anchor=north] at (12,0) {$x_N$};
    \node[BLACK, anchor=east] at (0,0) {$y_0$};
    \node[BLACK, anchor=east] at (0,1) {$y_1$};
    \node[BLACK, anchor=east] at (0,7) {$y_{M - 1}$};
    \node[BLACK, anchor=east] at (0,8) {$y_M$};
    \draw[BLACK, <->] (7,-0.2) -- (8,-0.2);
    \node[BLACK, below] at (7.5,-0.2) {$h$};
    \draw[BLACK, <->] (-0.2,4) -- (-0.2,5);
    \node[BLACK, left] at (-0.2,4.5) {$h$};
    \filldraw[RED] (6,4) circle (2.5pt) node[anchor=south west] {$V_{n,m}$};
    \draw[RED] (6,3) -- (6,4) -- (6,5);
    \draw[RED] (5,4)-- (6,4) -- (7,4);
    \filldraw[BLUE] (7,4) circle (2.5pt) node[anchor=north west] {$V_{n+1,m}$};
    \filldraw[BLUE] (5,4) circle (2.5pt) node[anchor=south east] {$V_{n-1,m}$};
    \filldraw[BLUE] (6,3) circle (2.5pt) node[anchor=north] {$V_{n,m+1}$};
    \filldraw[BLUE] (6,5) circle (2.5pt) node[anchor=south] {$V_{n,m-1}$};
    \draw[BLACK, <->] (0,8.3) -- (12,8.3);
    \node[BLACK, above] at (6,8.3) {$w$};
    \draw[BLACK, <->] (12.3,0) -- (12.3,8);
    \node[BLACK, right] at (12.3,4) {$\ell$};
\end{tikzpicture}
\caption{A two-dimensional lattice of points.}
\label{fig:latticegrid}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}
    \coordinate (vertex1) at (4,0);
    \coordinate (vertex2) at (2,3.464102);
    \coordinate (vertex3) at (-2,3.464102);
    \coordinate (vertex4) at (-4,0);
    \coordinate (vertex5) at (-2,-3.464102);
    \coordinate (vertex6) at (2,-3.464102);
    %
    \node at (vertex1) (nodeV1) {\Huge\circled{1}{ORANGE}{RED}{DARKBLUE}};
    \node at (vertex2) (nodeV2) {\Huge\circled{2}{ORANGE}{RED}{DARKBLUE}};
    \node at (vertex3) (nodeV3) {\Huge\circled{3}{ORANGE}{RED}{DARKBLUE}};
    \node at (vertex4) (nodeV4) {\Huge\circled{4}{ORANGE}{RED}{DARKBLUE}};
    \node at (vertex5) (nodeV5) {\Huge\circled{5}{ORANGE}{RED}{DARKBLUE}};
    \node at (vertex6) (nodeV6) {\Huge\circled{6}{ORANGE}{RED}{DARKBLUE}};
    %
    \draw[black, ultra thick, <->] (nodeV1) -- (nodeV2);
    \draw[black, ultra thick, ->] (nodeV2) -- (nodeV3);
    \draw[black, ultra thick, <->] (nodeV3) -- (nodeV4);
    \draw[black, ultra thick, ->] (nodeV4) -- (nodeV5);
    \draw[black, ultra thick, <->] (nodeV5) -- (nodeV6);
    \draw[black, ultra thick, <->] (nodeV1) -- (nodeV4);
    \draw[black, ultra thick, ->] (nodeV1) -- (nodeV3);
    \draw[black, ultra thick, ->] (nodeV4) -- (nodeV6);
\end{tikzpicture}
\end{figure}

@@

And the total eigenenergy is
\begin{equation}
    E_{n_x n_y n_z} = E_{n_x} + E_{n_y} + E_{n_z} = \hbar \omega \left( n_x + \frac{1}{2} \right) + \hbar \omega \left( n_y + \frac{1}{2} \right) + \hbar \omega \left( n_z + \frac{1}{2} \right) \label{eq:3dQHO:eigenenergy}
\end{equation}

@@

It follows from Eq. (\ref{eq:3dQHO:eigenenergy}) that the energy is strictly a function of $n$. That is, any combination of $n_x$, $n_y$, and $n_z$, as long as they produce the same $n$, will yield the same energy. Such states are said to be \emph{degenerate}. Our goal is to find how many possible combinations of $n_x$, $n_y$, and $n_z$ exist for a given $n$.

>>>>

This document is not a guide on how to use {\LaTeX}, since plenty of those already exist. Instead, what follows is an incoherent collection of examples that illustrate good practice. For more of my awesome {\LaTeX} resources, visit \url{https://github.com/nkostin4/LaTeX-templates}.

@@

It is not hard to show that the eigenvalues of a Hermitian operator are real. Let $\ket{a}$ be an eigenstate of the Hermitian operator $A$ corresponding to eigenvalue $a$, then
\begin{equation}
    A \ket{a} = a \ket{a}. \label{eqn:quantum:eigenvalueproblem}
\end{equation}

Then we have
\begin{equation}
    \braket{a|A|a} = \braket{a|a|a} = a\braket{a|a}. \label{eqn:quantum:1}
\end{equation}

Taking the Hermitian conjugate of both sides of (\ref{eqn:quantum:eigenvalueproblem}) gives
\begin{equation}
    \bra{a} A^{\dagger} = a^{*} \bra{a}.
\end{equation}

Then we also have
\begin{equation}
    \braket{a|A^{\dagger}|a} = a^{*} \braket{a|a} \label{eqn:quantum:2}
\end{equation}

Since $A$ is Hermitian, we have $\braket{a|A^{\dagger}|a} = \braket{a|A|a}$. Then comparing (\ref{eqn:quantum:1}) and (\ref{eqn:quantum:2}) gives
\begin{equation*}
    \left( a - a^* \right) \braket{a|a} = 0.
\end{equation*}

@@

\begin{figure}[H]
\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
\centering
\begin{tikzpicture}[xscale=1,yscale=1]
    % Draw outside rectangle
    \draw[BLACK] (-2,-2) rectangle (14,10);
    % Draw lattice points
    \foreach \a in {0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12}
    {
        \foreach \b in {0, 1, 2, 3, 4, 5, 6, 7, 8}
        {
            \filldraw[BLACK] (\a, \b) circle (2pt);
        }
    }
    \node[BLACK, anchor=north] at (0,0) {$x_0$};
    \node[BLACK, anchor=north] at (1,0) {$x_1$};
    \node[BLACK, anchor=north] at (11,0) {$x_{N - 1}$};
    \node[BLACK, anchor=north] at (12,0) {$x_N$};
    \node[BLACK, anchor=east] at (0,0) {$y_0$};
    \node[BLACK, anchor=east] at (0,1) {$y_1$};
    \node[BLACK, anchor=east] at (0,7) {$y_{M - 1}$};
    \node[BLACK, anchor=east] at (0,8) {$y_M$};
    \draw[BLACK, <->] (7,-0.2) -- (8,-0.2);
    \node[BLACK, below] at (7.5,-0.2) {$h$};
    \draw[BLACK, <->] (-0.2,4) -- (-0.2,5);
    \node[BLACK, left] at (-0.2,4.5) {$h$};
    \filldraw[RED] (6,4) circle (2.5pt) node[anchor=south west] {$V_{n,m}$};
    \draw[RED] (6,3) -- (6,4) -- (6,5);
    \draw[RED] (5,4)-- (6,4) -- (7,4);
    \filldraw[BLUE] (7,4) circle (2.5pt) node[anchor=north west] {$V_{n+1,m}$};
    \filldraw[BLUE] (5,4) circle (2.5pt) node[anchor=south east] {$V_{n-1,m}$};
    \filldraw[BLUE] (6,3) circle (2.5pt) node[anchor=north] {$V_{n,m+1}$};
    \filldraw[BLUE] (6,5) circle (2.5pt) node[anchor=south] {$V_{n,m-1}$};
    \draw[BLACK, <->] (0,8.3) -- (12,8.3);
    \node[BLACK, above] at (6,8.3) {$w$};
    \draw[BLACK, <->] (12.3,0) -- (12.3,8);
    \node[BLACK, right] at (12.3,4) {$\ell$};
\end{tikzpicture}
\caption{A two-dimensional lattice of points.}
\label{fig:latticegrid}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}
    \coordinate (vertex1) at (4,0);
    \coordinate (vertex2) at (2,3.464102);
    \coordinate (vertex3) at (-2,3.464102);
    \coordinate (vertex4) at (-4,0);
    \coordinate (vertex5) at (-2,-3.464102);
    \coordinate (vertex6) at (2,-3.464102);
    %
    \node at (vertex1) (nodeV1) {\Huge\circled{1}{ORANGE}{RED}{DARKBLUE}};
    \node at (vertex2) (nodeV2) {\Huge\circled{2}{ORANGE}{RED}{DARKBLUE}};
    \node at (vertex3) (nodeV3) {\Huge\circled{3}{ORANGE}{RED}{DARKBLUE}};
    \node at (vertex4) (nodeV4) {\Huge\circled{4}{ORANGE}{RED}{DARKBLUE}};
    \node at (vertex5) (nodeV5) {\Huge\circled{5}{ORANGE}{RED}{DARKBLUE}};
    \node at (vertex6) (nodeV6) {\Huge\circled{6}{ORANGE}{RED}{DARKBLUE}};
    %
    \draw[BLACK, ultra thick, <->] (nodeV1) -- (nodeV2);
    \draw[BLACK, ultra thick, ->] (nodeV2) -- (nodeV3);
    \draw[BLACK, ultra thick, <->] (nodeV3) -- (nodeV4);
    \draw[BLACK, ultra thick, ->] (nodeV4) -- (nodeV5);
    \draw[BLACK, ultra thick, <->] (nodeV5) -- (nodeV6);
    \draw[BLACK, ultra thick, <->] (nodeV1) -- (nodeV4);
    \draw[BLACK, ultra thick, ->] (nodeV1) -- (nodeV3);
    \draw[BLACK, ultra thick, ->] (nodeV4) -- (nodeV6);
\end{tikzpicture}
\end{figure}

@@

And the total eigenenergy is
\begin{equation}
    E_{n_x n_y n_z} = E_{n_x} + E_{n_y} + E_{n_z} = \hbar \omega \left( n_x + \frac{1}{2} \right) + \hbar \omega \left( n_y + \frac{1}{2} \right) + \hbar \omega \left( n_z + \frac{1}{2} \right) \label{eqn:3dQHO:eigenenergy}
\end{equation}

@@

It follows from Eq. (\ref{eqn:3dQHO:eigenenergy}) that the energy is strictly a function of $n$. That is, any combination of $n_x$, $n_y$, and $n_z$, as long as they produce the same $n$, will yield the same energy. Such states are said to be \emph{degenerate}. Our goal is to find how many possible combinations of $n_x$, $n_y$, and $n_z$ exist for a given $n$.
